A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-12-02 bioc-workflow.tex
updates based on Claire's comments - up to p13

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 17:06:03 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 17:06:03 2016 
## Subset [6725,20][5032,20] Fri Dec  2 17:06:04 2016 
## Removed features with more than 0 NAs: Fri Dec  2 17:06:04 2016 
## Dropped featureData's levels Fri Dec  2 17:06:04 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

It is also useful to visualise the relative intensities along the
gradient to identify channels displaying particularly low yield. This
can be done using the \texttt{plotDist} and \texttt{boxplot}
functions, that plot the protein profiles occupancy along the gradient
(we also display the mean channel intensities) and a \texttt{boxplot}
of the column intensities.  In the two plots displayed on figure
\ref{fig:qcbx}, we re-order the TMT channles to pair corresponding
channels in the two replicates (rather than ordering the channels by
replicate).

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{par}\hlstd{(}\hlkwc{mfrow} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{2}\hlstd{))}
\hlstd{o} \hlkwb{<-} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)}
\hlkwd{plotDist}\hlstd{(hl[, o],} \hlkwc{pcol} \hlstd{=} \hlstr{"#00000010"}\hlstd{)}
\hlkwd{lines}\hlstd{(}\hlkwd{colMeans}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o])),} \hlkwc{col} \hlstd{=} \hlstr{"red"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"b"}\hlstd{)}
\hlkwd{boxplot}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o]),} \hlkwc{las} \hlstd{=} \hlnum{2}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=\textwidth]{figure/qcbx-1}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Fri Dec  2 17:06:06 2016 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Dec  2 17:06:07 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Fri Dec  2 17:06:05 2016 
## Added markers from  'pdres' marker vector. Fri Dec  2 17:06:07 2016 
##  MSnbase version: 2.1.4
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4350585               0.3020114               0.3827713 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6916987               0.5981016               0.4325049 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4337431               0.5912701               0.9497307 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7942905               0.7137491               0.3148182 
##         Plasma membrane              Proteasome 
##               0.7173760               0.4123604
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      86                     169                      88 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     297                     477                      98 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      28                     123                     522 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     342                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     318                     158                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{sessionInfo}\hlstd{()}
\end{alltt}
\begin{verbatim}
## R version 3.3.2 Patched (2016-11-01 r71616)
## Platform: x86_64-pc-linux-gnu (64-bit)
## Running under: Ubuntu 14.04.5 LTS
## 
## locale:
##  [1] LC_CTYPE=en_GB.UTF-8       LC_NUMERIC=C              
##  [3] LC_TIME=en_GB.UTF-8        LC_COLLATE=en_GB.UTF-8    
##  [5] LC_MONETARY=en_GB.UTF-8    LC_MESSAGES=en_GB.UTF-8   
##  [7] LC_PAPER=en_GB.UTF-8       LC_NAME=C                 
##  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
## [11] LC_MEASUREMENT=en_GB.UTF-8 LC_IDENTIFICATION=C       
## 
## attached base packages:
## [1] stats4    parallel  methods   stats     graphics  grDevices utils    
## [8] datasets  base     
## 
## other attached packages:
##  [1] pRolocdata_1.12.0    pRoloc_1.15.5        MLInterfaces_1.54.0 
##  [4] cluster_2.0.5        annotate_1.52.0      XML_3.98-1.4        
##  [7] AnnotationDbi_1.36.0 IRanges_2.8.0        S4Vectors_0.12.0    
## [10] MSnbase_2.1.4        ProtGenerics_1.6.0   BiocParallel_1.8.1  
## [13] mzR_2.8.0            Rcpp_0.12.7          Biobase_2.34.0      
## [16] BiocGenerics_0.20.0  gridExtra_2.2.1      xtable_1.8-2        
## [19] BiocStyle_2.2.1      knitr_1.14          
## 
## loaded via a namespace (and not attached):
##   [1] minqa_1.2.4           colorspace_1.3-1      hwriter_1.3.2        
##   [4] class_7.3-14          modeltools_0.2-21     mclust_5.2           
##   [7] pls_2.5-0             base64enc_0.1-3       proxy_0.4-16         
##  [10] hexbin_1.27.1         MatrixModels_0.4-1    affyio_1.44.0        
##  [13] flexmix_2.3-13        mvtnorm_1.0-5         codetools_0.2-15     
##  [16] splines_3.3.2         doParallel_1.0.10     impute_1.48.0        
##  [19] robustbase_0.92-6     jsonlite_1.1          nloptr_1.0.4         
##  [22] caret_6.0-72          pbkrtest_0.4-6        rda_1.0.2-2          
##  [25] kernlab_0.9-25        vsn_3.42.3            sfsmisc_1.1-0        
##  [28] shiny_0.14.2          sampling_2.7          assertthat_0.1       
##  [31] Matrix_1.2-7.1        limma_3.30.2          formatR_1.4          
##  [34] htmltools_0.3.5       quantreg_5.29         tools_3.3.2          
##  [37] ggvis_0.4.3           gtable_0.2.0          affy_1.52.0          
##  [40] reshape2_1.4.2        dplyr_0.5.0           MALDIquant_1.15      
##  [43] trimcluster_0.1-2     gdata_2.17.0          preprocessCore_1.36.0
##  [46] nlme_3.1-128          iterators_1.0.8       fpc_2.1-10           
##  [49] stringr_1.1.0         lme4_1.1-12           lpSolve_5.6.13       
##  [52] mime_0.5              gtools_3.5.0          dendextend_1.3.0     
##  [55] DEoptimR_1.0-6        zlibbioc_1.20.0       MASS_7.3-45          
##  [58] scales_0.4.0          BiocInstaller_1.24.0  pcaMethods_1.66.0    
##  [61] SparseM_1.72          RColorBrewer_1.1-2    ggplot2_2.1.0        
##  [64] biomaRt_2.30.0        rpart_4.1-10          stringi_1.1.2        
##  [67] RSQLite_1.0.0         highr_0.6             genefilter_1.56.0    
##  [70] randomForest_4.6-12   foreach_1.4.3         e1071_1.6-7          
##  [73] prabclus_2.2-6        bitops_1.0-6          mzID_1.12.0          
##  [76] evaluate_0.10         lattice_0.20-34       htmlwidgets_0.7      
##  [79] gbm_2.1.1             plyr_1.8.4            magrittr_1.5         
##  [82] R6_2.2.0              DBI_0.5-1             whisker_0.3-2        
##  [85] mgcv_1.8-15           survival_2.40-1       RCurl_1.95-4.8       
##  [88] nnet_7.3-12           tibble_1.2            msdata_0.14.0        
##  [91] car_2.1-3             mlbench_2.1-1         grid_3.3.2           
##  [94] FNN_1.1               ModelMetrics_1.1.0    threejs_0.2.2        
##  [97] digest_0.6.10         diptest_0.75-7        httpuv_1.3.3         
## [100] munsell_0.4.3
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 17:19:06 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 17:19:06 2016 
## Subset [6725,20][5032,20] Fri Dec  2 17:19:07 2016 
## Removed features with more than 0 NAs: Fri Dec  2 17:19:07 2016 
## Dropped featureData's levels Fri Dec  2 17:19:07 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

It is also useful to visualise the relative intensities along the
gradient to identify channels displaying particularly low yield. This
can be done using the \texttt{plotDist} and \texttt{boxplot}
functions, that plot the protein profiles occupancy along the gradient
(we also display the mean channel intensities) and a \texttt{boxplot}
of the column intensities.  In the two plots displayed on figure
\ref{fig:qcbx}, we re-order the TMT channels to pair corresponding
channels in the two replicates (rather than ordering the channels by
replicate).

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{par}\hlstd{(}\hlkwc{mfrow} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{2}\hlstd{))} \hlcom{## creates a two-panel figure}
\hlstd{o} \hlkwb{<-} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)}
\hlkwd{plotDist}\hlstd{(hl[, o],} \hlkwc{pcol} \hlstd{=} \hlstr{"#00000010"}\hlstd{)}
\hlkwd{lines}\hlstd{(}\hlkwd{colMeans}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o])),} \hlkwc{col} \hlstd{=} \hlstr{"red"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"b"}\hlstd{)}
\hlkwd{boxplot}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o]),} \hlkwc{las} \hlstd{=} \hlnum{2}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=\textwidth]{figure/qcbx-1}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Fri Dec  2 17:19:09 2016 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Dec  2 17:19:09 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Fri Dec  2 17:19:08 2016 
## Added markers from  'pdres' marker vector. Fri Dec  2 17:19:09 2016 
##  MSnbase version: 2.1.4
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4368179               0.3037653               0.3856993 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6916475               0.5951696               0.4377555 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4317514               0.5919750               0.9527663 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7947663               0.7096575               0.3269003 
##         Plasma membrane              Proteasome 
##               0.7210996               0.4155492
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     172                      88 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     296                     477                     100 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     123                     513 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     231                     344                      42 
##         Plasma membrane              Proteasome                 unknown 
##                     318                     157                    2059
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{sessionInfo}\hlstd{()}
\end{alltt}
\begin{verbatim}
## R version 3.3.2 Patched (2016-11-01 r71616)
## Platform: x86_64-pc-linux-gnu (64-bit)
## Running under: Ubuntu 14.04.5 LTS
## 
## locale:
##  [1] LC_CTYPE=en_GB.UTF-8       LC_NUMERIC=C              
##  [3] LC_TIME=en_GB.UTF-8        LC_COLLATE=en_GB.UTF-8    
##  [5] LC_MONETARY=en_GB.UTF-8    LC_MESSAGES=en_GB.UTF-8   
##  [7] LC_PAPER=en_GB.UTF-8       LC_NAME=C                 
##  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
## [11] LC_MEASUREMENT=en_GB.UTF-8 LC_IDENTIFICATION=C       
## 
## attached base packages:
## [1] stats4    parallel  methods   stats     graphics  grDevices utils    
## [8] datasets  base     
## 
## other attached packages:
##  [1] pRolocdata_1.12.0    pRoloc_1.15.5        MLInterfaces_1.54.0 
##  [4] cluster_2.0.5        annotate_1.52.0      XML_3.98-1.5        
##  [7] AnnotationDbi_1.36.0 IRanges_2.8.1        S4Vectors_0.12.1    
## [10] MSnbase_2.1.4        ProtGenerics_1.6.0   BiocParallel_1.8.1  
## [13] mzR_2.8.0            Rcpp_0.12.8          Biobase_2.34.0      
## [16] BiocGenerics_0.20.0  gridExtra_2.2.1      xtable_1.8-2        
## [19] BiocStyle_2.2.1      knitr_1.15.1        
## 
## loaded via a namespace (and not attached):
##   [1] minqa_1.2.4           colorspace_1.3-1      hwriter_1.3.2        
##   [4] class_7.3-14          modeltools_0.2-21     mclust_5.2           
##   [7] pls_2.5-0             base64enc_0.1-3       proxy_0.4-16         
##  [10] hexbin_1.27.1         MatrixModels_0.4-1    affyio_1.44.0        
##  [13] flexmix_2.3-13        mvtnorm_1.0-5         codetools_0.2-15     
##  [16] splines_3.3.2         doParallel_1.0.10     impute_1.48.0        
##  [19] robustbase_0.92-6     jsonlite_1.1          nloptr_1.0.4         
##  [22] caret_6.0-73          pbkrtest_0.4-6        rda_1.0.2-2          
##  [25] kernlab_0.9-25        vsn_3.42.3            sfsmisc_1.1-0        
##  [28] shiny_0.14.2          sampling_2.7          assertthat_0.1       
##  [31] Matrix_1.2-7.1        lazyeval_0.2.0        limma_3.30.6         
##  [34] htmltools_0.3.5       quantreg_5.29         tools_3.3.2          
##  [37] ggvis_0.4.3           gtable_0.2.0          affy_1.52.0          
##  [40] reshape2_1.4.2        dplyr_0.5.0           MALDIquant_1.15      
##  [43] trimcluster_0.1-2     gdata_2.17.0          preprocessCore_1.36.0
##  [46] nlme_3.1-128          iterators_1.0.8       fpc_2.1-10           
##  [49] stringr_1.1.0         lme4_1.1-12           lpSolve_5.6.13       
##  [52] mime_0.5              gtools_3.5.0          dendextend_1.3.0     
##  [55] DEoptimR_1.0-8        zlibbioc_1.20.0       MASS_7.3-45          
##  [58] scales_0.4.1          BiocInstaller_1.24.0  pcaMethods_1.66.0    
##  [61] SparseM_1.74          RColorBrewer_1.1-2    memoise_1.0.0        
##  [64] ggplot2_2.2.0         biomaRt_2.30.0        rpart_4.1-10         
##  [67] stringi_1.1.2         RSQLite_1.1           highr_0.6            
##  [70] genefilter_1.56.0     randomForest_4.6-12   foreach_1.4.3        
##  [73] e1071_1.6-7           prabclus_2.2-6        bitops_1.0-6         
##  [76] mzID_1.12.0           evaluate_0.10         lattice_0.20-34      
##  [79] htmlwidgets_0.8       gbm_2.1.1             plyr_1.8.4           
##  [82] magrittr_1.5          R6_2.2.0              DBI_0.5-1            
##  [85] whisker_0.3-2         mgcv_1.8-16           survival_2.40-1      
##  [88] RCurl_1.95-4.8        nnet_7.3-12           tibble_1.2           
##  [91] msdata_0.14.0         car_2.1-3             mlbench_2.1-1        
##  [94] grid_3.3.2            FNN_1.1               ModelMetrics_1.1.0   
##  [97] threejs_0.2.2         digest_0.6.10         diptest_0.75-7       
## [100] httpuv_1.3.3          munsell_0.4.3
\end{verbatim}
\end{kframe}
\end{knitrout}
